Databrary: A digital data library for sharing research video

### 2015-01-18 jcdl-15/paper.tex
Add technical infrastructure paragraph
Needs citations, though that goes without saying since everything does

Finally, records can be attached not only to entire sessions, but also to arbitrary temporal sub-sets of a session.
That is, if any record only applies to part of a session, for example a single activity, or a participant being present for only part of a recording, it can be applied within the timeline of a session to only the appropriate part.
This allows the final type of organizational structure, wherein records define virtual sub-sessions that can be grouped and interacted with as units, without needing to cut up source videos.
It also can be used to represent annotations at a finer temporal scale, for example individual events interactions that are normally handled by off-line annotation softaware.
However, the appropriate interfaces and tools to input or import these annotations are still being developed.

%\subsection{Technical infrastructure}

@@

@@

As the extant research data libraries demonstrate, there is always the tension between standardization and flexibility.
Since we're primarily dealing with video and audio data, we have, without much loss of flexibility, standardized on a particular encoding format (codecs and parameters) that allows for convenient access and HTML5-based streaming, while still allowing arbitrary resolutions and sample/frame-rates.
We also allow for ``dumps'', which allow users - using certain portable data formats (e.g. ...) - to include any data that cannot be encompassed by our standard formats. In this way, we can incorporate data which may be relevant for re-use, but not broadly adopted by the community, without making the system too rigid.

@@

\section{Conclusion}

\section{Acknowledgments}

>>>>

Finally, records can be attached not only to entire sessions, but also to arbitrary temporal sub-sets of a session.
That is, if any record only applies to part of a session, for example a single activity, or a participant being present for only part of a recording, it can be applied within the timeline of a session to only the appropriate part.
This allows the final type of organizational structure, wherein records define virtual sub-sessions that can be grouped and interacted with as units, without needing to cut up source videos.
It also can be used to represent annotations at a finer temporal scale, for example individual events interactions that are normally handled by off-line annotation software.
However, the appropriate interfaces and tools to input or import these annotations are still being developed.

\subsection{Technical infrastructure}

@@

Databrary is a new, cohesive web application, built on the Play Framework to enable a responsive user interface, a complete API, and high-performance streaming.
Recordings and other files are placed in content-based filesystem storage, and all structured data are stored in a PostgreSQL database, leveraging its geometric indexing capabilities for temporal data.
All uploaded recordings are automatically transcoded to a standard format to enable cross-platform HTML5-based streaming and downloading for off-line access, currently H.264/AAC in an MPEG-4 container for video.
This transcoding utilizes the high performance computing cluster at the hosting campus of New York University, using ffmpeg's libav bindings for both this and direct access to video frames and clips.
The user interface is built primarily on the Angular web framework, and all data access is performed through an open JSON API.
Although hosted data are protected, all source code is released under a GPLv3 license on github.

@@

As the extant research data libraries demonstrate, there is always the tension between standardization and flexibility.
Since we're primarily dealing with video and audio data, standardizing on an encoding format allows for convenient, consistent access without much loss of flexibility, while still allowing arbitrary resolutions, encoding qualities, and sample/frame-rates.
We also allow for ``dumps'', which allow users---using certain portable data formats (e.g. ...)---to include any data that cannot be encompassed by our standard formats. In this way, we can incorporate data which may be relevant for re-use, but not broadly adopted by the community, without making the system too rigid.

@@

\section{Conclusions}

\section*{Acknowledgments}
